---
title: "Peer-graded Assignment: R Markdown and Leaflet"
author: "Jeffrey M. Hunter"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    toc: no
    toc_float: yes
    theme: cosmo
    keep_md: no
    df_print: paged
  pdf_document:
    toc: yes
    df_print: kable
    number_sections: false
    fig_caption: yes
    highlight: tango
    dev: pdf
  word_document:
    toc: yes
    df_print: paged
    keep_md: no
---

## Synopsis

This webpage was created for the Developing Data Products course as part of the
Data Science Specialization offered through Coursera from Johns Hopkins
University.

## My Hot Wing Locations

The page was built in RStudio using R Markdown and the Leaflet package to
build an interactive map of my favorite hot wing locations. Attempting to
explain my addiction to really good hot wings is beyond the scope of this
assignment. And yes, it is an addiction!

The source code for this project can be found on
GitHub: <a target="_blank" href="https://github.com/oraclejavanet/developing-data-products-course-project-1">Developing Data Products Course Project 1</a>

```{r setup, include = FALSE}
# set knitr options
knitr::opts_chunk$set(echo = TRUE, fig.path = 'figures/')

# clear the global workspace (including hidden objects)
rm(list = ls(all.names = TRUE))

# set working directory
setwd("~/repos/coursera/github-assignments/developing-data-products-course-project-1")

# free up memory and display statistics on free memory
gc()
```

```{r hot-wing-locations-map, message = FALSE, echo = TRUE}
library(knitr)
library(leaflet)

hwIcon <- makeIcon(
  iconUrl = "images/buffalo-wing.png",
  iconWidth = 25,
  iconHeight = 50
)

hwLocations <- data.frame(name = c("Quaker Steak",
                                   "Buffalo Wild Wings",
                                   "Villa Grande"),
                          lat = c(40.684667,
                                  40.45082,
                                  40.867617),
                          lng = c(-80.109943,
                                  -80.182565,
                                  -79.922441))

hwPopup <- c(
  "<a href = 'http://thelube.com/' target = '_blank'>Quaker Steak and Lube</a>",
  "<a href = 'https://www.buffalowildwings.com/' target = '_blank'>Buffalo Wild Wings</a>",
  "<a href = 'http://www.villagrandeonline.com/' target = '_blank'>Villa Grande</a>"
)

hwLocations %>%
  leaflet() %>%
  addTiles() %>%
  addMarkers(icon = hwIcon, popup = hwPopup)
```
